NoTitle

### 2017-06-13 Aplas17/paper.tex
Abstract typos.

\begin{abstract}
Multiple inheritance is a valuable feature for Object-Oriented
Programming. However it is also tricky to get right, as illustrated by
the extensive literature on the topic. One of the most promising 
approaches to multiple inheritance are traits. Traits offer a
restricted model of multiple inheritance that is easy to reason and 
has many elegant properties. Traits have good support for method 
conflicts which arize from \emph{diamond inheritance}:
conflicts that arize from method implementations sharing a common 
ancestor. However the mechanisms of traits are inadequate to deal 
with \emph{unintentional method conflicts}: conflicts which 
arize from two unrelated methods that happen to share the same name
and signature.

This paper presents a new trait model that deals with unintended
method conflicts. In our new trait model conflicting methods arizing
from unrelated methods can coexist in the same trait. Moreover they
can be \emph{independently overriden}. What ensures unambiguity 
is the use of information about the class hierarchy. In turn
hierarchical information is also employed in method dispatching, which 
uses a combination of static and dynamic type information to chose 
the implementation of a method at run-time. We give illustrative 
examples of our language and features and formalize a minimal 
Featherweight-Java style calculus.

>>>>

\begin{abstract}
Multiple inheritance is a valuable feature for Object-Oriented
Programming. However it is also tricky to get right, as illustrated by
the extensive literature on the topic. One of the most promising 
approaches to multiple inheritance are traits. Traits offer a
restricted model of multiple inheritance that is easy to reason and 
has many elegant properties. Traits have good support for method 
conflicts which arise from \emph{diamond inheritance}:
conflicts that arise from method implementations sharing a common 
ancestor. However the mechanisms of traits are inadequate to deal 
with \emph{unintentional method conflicts}: conflicts which 
arise from two unrelated methods that happen to share the same name
and signature.

This paper presents a new trait model that deals with unintended
method conflicts. In our new trait model conflicting methods arising
from unrelated methods can coexist in the same trait. Moreover they
can be \emph{independently overridden}. What ensures unambiguity 
is the use of information about the class hierarchy. In turn
hierarchical information is also employed in method dispatching, which 
uses a combination of static and dynamic type information to choose 
the implementation of a method at run-time. We give illustrative 
examples of our language and features and formalize a minimal 
Featherweight-Java style calculus.
